|

### 2020-06-13 appendix/appendix_final.Rmd
commit appendix 4

```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F}
f <- ggarrange(f1, f3, f5, 
               ggplot() + theme_void(), f4, f6, 
               f2, ggplot() + theme_void(), f7,
               ncol = 3, nrow = 3, 
               hjust = 0, align = 'hv')
ggsave("./plots/fig.pdf", plot = f, width = 35, height = 25, units = "cm")
```

\newpage
# Meta-Analysis (all coefficients) {#full-meta-an}

>>>>

```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F}
f <- ggarrange(f1, f3, f5, 
               f4, f6,
               f2, f7,
               ncol = 3, nrow = 3, 
               hjust = 0, align = 'hv')
ggsave("./plots/fig.pdf", plot = f, width = 35, height = 25, units = "cm")
f <- ggarrange(f1, f4, f2,
               f3, f6, 
               f7, f5,
               ncol = 3, nrow = 3, 
               hjust = 0, align = 'hv')
ggsave("./plots/fig2.pdf", plot = f, width = 35, height = 25, units = "cm")
```

# Meta-Analysis (all coefficients) {#full-meta-an}
